Coherent optical association of a single molecule

### 2020-09-30 paper.tex
Clean up, regenerate pdf
Update on Overleaf.

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $50 \%$ \todo{number}.
  The molecule has a (change to 8.8G) zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
  and lifetime up to $1 \mathrm{ms}$ \todo{number}. (center of mass motional state population.)
  % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
  This technique is general (does not rely on narrow excited state linewidth) and could allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

% 1. we want to have a diverse species to tailor to different applications including precision measurements and quantum engineering. 2. for the technique of associating atoms to form molecules, but so far all has been done with Feshbach association (before STIRAP), or in the case of Sr2, a narrow excited state. Previous work on near-threshold Raman transfer has been incoherent.
%(suggested referees: Florian Shreck and Immanual Bloch, Tanya, Deep Gupta, DeMille)

%Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).

Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules  below 1~mK~\cite{Norrgard2016}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the associations of ultracold atoms.
%(any place to cite  molecular ion work?)
% cite recent doyle group result on cooling symmetric top molecule? FOR SURE, and other laser cooling works and electro-optical-cooling! Citations are not complete. Add them as you see fit.

@@

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state, schematically shown in Fig.~\ref{f-theory}A. The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.  Our scheme is based on using a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best transfer Rabi coupling to photon scattering ratio. To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible. This approach minimizes the reliance on system specific properties and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
%(also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))

%This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
%electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering. Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.

%Production of ultracold molecules in optical tweezers is challenging due to their internal degrees of freedom including rotation and vibration. In certain molecular species with relatively closed cycling transitions, direct laser cooling remains a viable option. However, for many species, including NaCs, the vibrational branching ratios are unfavorable, making direct laser cooling challenging. In these systems, a bottom-up approach of assembling the molecule from its constituent atoms has been demonstrated both in bulk gas and in optical tweezers. The challenge in a bottom-up approach is the vastly different length scales between the free atoms and a ground state molecule, leading to small coupling between them. For atoms in the motional ground state in the tweezer, the average distance between the two atoms is about $1000a_0$. However, for the ground rovibrational molecule, the bond length is only around $4a_0$. Because of this, it is necessary to use an intermediate state with a size in between the initial and final states, and accomplish the transfer in two steps in order to increase the coupling.

%The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance \todo{cite our FB result}. However, this requires a suitable Feshbach resonance, which limits the generality of this technique. An alternative approach uses a weakly bound ground electronic molecular state as the intermediate state (I'm wondering how we can distinguish this weakly bound molecular state from the weakly-bound Feshbach molecule state, we can maybe specify typcial binding energies? "most weakly bound state of the low field ground state electronic potential" maybe?), populated by an optical Raman transition, schematically shown in figure \todo{}. In this scheme, a pair of Raman beams is used to drive the unbound, but confined, atoms to a bound molecular state via an excited molecular state. This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules. Such a transfer using an optical transition has been observed in previous experiments \todo{cite}. However, they either require the use of a narrow optical transition which limits the generality or were driving the transition incoherently due to scattering.

@@

%While optical Raman transfers of atoms to molecules utilizing an electronic excited state have been shown previously, the transfers were incoherent  where the resulting molecules were lost~\cite{Wynar2000,Rom2004}.
%For a given excited intermediate state,
%This can be understood by using a three level model.
%However, we are constrained by the multi-level of molecules.
%A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced. In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $. To understand the effect of this imbalance, we consider a 3 level model, and ignore the presence of multiple excited states.

%The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state. While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
%Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.

In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}A), we consider the initial atomic state, the target weakly-bound molecular state coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The Raman Rabi Rate for a detuned transfer, $ \Omega_a\Omega_m / 2\Delta$ depends on both of these matrix elements and the single photon detuning. Unlike for Raman transitions in atoms, the two matrix elements, $ \Omega_m$ and $ \Omega_a$ are greatly imbalanced. Since $ \Omega_m $ is generally much larger than $ \Omega_a $ due to the wavefunction mismatch between the atomic state and the excited molecular state, the scattering rate predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth. We choose the power of the Raman beams to be equal (which gives the largest Raman Rabi rate at a fixed total power), so there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning. Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, larger detuning is preferred. However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency. With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates becomes a sum of the scattering rates and Rabi rates over all the states, and there are many possible intermediate states to choose from.

Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency. However, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}. For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning. Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)

To obtain a complete picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM). As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states.  %Since for a typical molecular potential the spacing between states
%decreases with increasing vibrational levels,
%a weakly bound excited molecular state
% This further increases the scattering rate for a weakly bond excited state.
%Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
%we found a distinct optimal regime from what has been explored experimentally previously.
Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state. As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) to drive the Raman transition. (mention the trend, also v=12 will work as similarly as v=0)

%higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states. As a result, we use a deeply bound molecular excited state to drive the Raman transition.

%(goes to SM?)

(mention scattering/lightshift depends on up/down matrix element ratio?)

%In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.  Thus, a small $ \Omega_m/\Omega_a $ ratio is desired to be able to drive this transition coherently at smaller detunings where the Raman Rabi frequency will be larger. In addition to this fundamental reason, there is also a technical advantage for having a $ \Omega_m/\Omega_a $ ratio to be as small( KW: I think small, but open question whether we should always talk about $\Omega_m/\Omega_a$ or $ \Omega_a/\Omega_m$, KN: maybe $ \Omega_a/\Omega_m$ is better because it sounds more natural that we want to make it large? but either way.) as possible. The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth. This becomes technically easier when $ \Omega_m/\Omega_a $ is smaller.
%(for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%. KW: I mentioned this in next paragraph, does it still need to be mentioned here?)

In addition to the intermediate state, the choice of the initial and final states is critical. As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the overall Raman Rabi Rate. This ratio can be made larger by increasing the coupling of the atomic state with the excited molecular state. Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. In addition to the confinement, this value is related to the interaction between the two atoms. For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C). The increase in the coupling is proportional to (quote/cite Olive's equation?). For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $\abs{a_{4422}}= 30.4a_0, \abs{a_{3311}} = 13.7a_0 $ respectively and 3322 has a large and negative scattering length of $ \abs{a_{3322}} = 693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}. In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly this spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states. Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth. Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.  Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination. (We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

@@

%% Preparation
To perform the Raman transfer, we use our apparatus described in our previous work~\cite{Liu2019}. Our experiment begins by loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers. The atoms are imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom during post selection. We then perform simultaneous Raman sideband cooling (RSC) to cool both atoms into the 3-dimensional motional ground state of their optical tweezers. After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off rso that the Na and Cs atoms are merged into the same tweezer \todo{cite}. The spin states for the Na and Cs atoms after RSC and during the merge process are $|F=2,m_F=2\rangle$ and $|F=4,m_F=4\rangle$ respectively. This states combination has a low scattering length of $... a_0$ which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.

After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length 3322 hyperfine combination. To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $|F=3,m_F=3\rangle$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer. This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of relative motional ground state.

@@

%% Transfer scheme
After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer. The pulse sequence for this step is shown in Fig.~\ref{f-raman}B. Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time (also minimize source of scattering). After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
\todo{clarify coprop of Raman beam?}

@@

The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}?). The up leg matrix element scales with the short length atomic wavefunction amplitude which is 0.375 for weakly interaction particles. However, due to the strong interaction between the two atoms, this approximation breaks down. Instead, theory calculation shows that the scaling is very well approximated by a power of 0.29 within the range of confinement in our experiment. Combined with the intensity factor of the Raman beams, the Raman Rabi frequency should scale with 1.29 power of the tweezer intensity, which agrees with our experimental result. Similar to the light shift, there is also a background component and a $v=0$ component in the Raman Rabi frequency. The $v=0$ component predicts a up leg Rabi frequency of $...$ which is consistent with theory. Unfortunately, the background Raman Rabi frequency cancels the Rabi frequency for red detuning Raman transition which is one of the factors that decreases our transfer efficiency. (need blue side?)

>>>>

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $50 \%$ \todo{number}.
  The molecule has a (change to 8.8G) zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
  and lifetime up to $1 \mathrm{ms}$ \todo{number}. (center of mass motional state population.)
  % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
  This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

% 1. we want to have a diverse species to tailor to different applications including precision measurements and quantum engineering. 2. for the technique of associating atoms to form molecules, but so far all has been done with Feshbach association (before STIRAP), or in the case of Sr2, a narrow excited state. Previous work on near-threshold Raman transfer has been incoherent.
% (suggested referees: Florian Shreck and Immanual Bloch, Tanya, Deep Gupta, DeMille)

% Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).

Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111}.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016, Mitra1366}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the association of ultracold atoms.
% (any place to cite  molecular ion work?)
% cite recent doyle group result on cooling symmetric top molecule? FOR SURE, and other laser cooling works and electro-optical-cooling! Citations are not complete. Add them as you see fit.

@@

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state, schematically shown in Fig.~\ref{f-theory}A. The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.  Our scheme is based on using a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best raman Rabi frequency to photon scattering ratio. To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible. This approach minimizes the reliance on system specific properties and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
% (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))

% This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules.
% electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering. Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.

% Production of ultracold molecules in optical tweezers is challenging due to their internal degrees of freedom including rotation and vibration. In certain molecular species with relatively closed cycling transitions, direct laser cooling remains a viable option. However, for many species, including NaCs, the vibrational branching ratios are unfavorable, making direct laser cooling challenging. In these systems, a bottom-up approach of assembling the molecule from its constituent atoms has been demonstrated both in bulk gas and in optical tweezers. The challenge in a bottom-up approach is the vastly different length scales between the free atoms and a ground state molecule, leading to small coupling between them. For atoms in the motional ground state in the tweezer, the average distance between the two atoms is about $1000a_0$. However, for the ground rovibrational molecule, the bond length is only around $4a_0$. Because of this, it is necessary to use an intermediate state with a size in between the initial and final states, and accomplish the transfer in two steps in order to increase the coupling.

% The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance \todo{cite our FB result}. However, this requires a suitable Feshbach resonance, which limits the generality of this technique. An alternative approach uses a weakly bound ground electronic molecular state as the intermediate state (I'm wondering how we can distinguish this weakly bound molecular state from the weakly-bound Feshbach molecule state, we can maybe specify typcial binding energies? "most weakly bound state of the low field ground state electronic potential" maybe?), populated by an optical Raman transition, schematically shown in figure \todo{}. In this scheme, a pair of Raman beams is used to drive the unbound, but confined, atoms to a bound molecular state via an excited molecular state. This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules. Such a transfer using an optical transition has been observed in previous experiments \todo{cite}. However, they either require the use of a narrow optical transition which limits the generality or were driving the transition incoherently due to scattering.

@@

% While optical Raman transfers of atoms to molecules utilizing an electronic excited state have been shown previously, the transfers were incoherent  where the resulting molecules were lost~\cite{Wynar2000,Rom2004}.
% For a given excited intermediate state,
% This can be understood by using a three level model.
% However, we are constrained by the multi-level of molecules.
% A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced. In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $. To understand the effect of this imbalance, we consider a 3 level model, and ignore the presence of multiple excited states.

% The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state. While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
% Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}. 
Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $ 
due to the small wavefunction overlap between the atomic state and the excited molecular state. The scattering rate therefore predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth. Because the energy difference of the atomic and the weakly bound states are small ($<$1~GHz) comparing to $\Delta$, the power of the Raman beams are chosen to be equal to gives the largest Raman Rabi rate at a fixed total power.) There is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning. Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, larger detuning is preferred. However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency. With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates become a sum of the scattering rates and Rabi rates over all the states. There are also many possible intermediate states to choose from.

Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency. However, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}. For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning. Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold. 
%(Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)

To obtain a complete picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM). As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states.  %Since for a typical molecular potential the spacing between states
% decreases with increasing vibrational levels,
% a weakly bound excited molecular state
% This further increases the scattering rate for a weakly bond excited state.
% Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
% we found a distinct optimal regime from what has been explored experimentally previously.
Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state. As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) to drive the Raman transition. (mention the trend, also v=12 will work as similarly as v=0)

% higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states. As a result, we use a deeply bound molecular excited state to drive the Raman transition.

% (goes to SM?)

%(mention scattering/lightshift depends on up/down matrix element ratio?)

% In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons.  Thus, a small $ \Omega_m/\Omega_a $ ratio is desired to be able to drive this transition coherently at smaller detunings where the Raman Rabi frequency will be larger. In addition to this fundamental reason, there is also a technical advantage for having a $ \Omega_m/\Omega_a $ ratio to be as small( KW: I think small, but open question whether we should always talk about $\Omega_m/\Omega_a$ or $ \Omega_a/\Omega_m$, KN: maybe $ \Omega_a/\Omega_m$ is better because it sounds more natural that we want to make it large? but either way.) as possible. The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth. This becomes technically easier when $ \Omega_m/\Omega_a $ is smaller.
% (for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%. KW: I mentioned this in next paragraph, does it still need to be mentioned here?)

In addition to the intermediate state, the choice of the initial and final states is critical. As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate. This ratio can be made larger by increasing the coupling of the atomic state with the excited molecular state. Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. In addition to the confinement, this value is related to the interaction between the two atoms. For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C). The increase in the coupling is proportional to (quote/cite Olive's equation?). For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $ a_{4422}= 30.4a_0, a_{3311} = 13.7a_0 $ respectively, but the 3332 combination has a large and negative scattering length of $ a_{3322} = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}. In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in the 3322 spin combinationn also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states. Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth. Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.  Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination. (We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

@@

%% Preparation
To perform the Raman transfer, we use our apparatus described in our previous work~\cite{Liu2019}. Our experiment begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers. The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom in order to perform post selection. We then perform simultaneous Raman sideband cooling (RSC) to cool both atoms into the 3-dimensional motional ground state of their optical tweezers. After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off, so that the Na and Cs atoms are merged into the same tweezer~\cite{Liu2019}. The spin states for the Na and Cs atoms after RSC and during the merge process are $|F=2,m_F=2\rangle_{Na}$ and $|F=4,m_F=4\rangle_{Cs}$ respectively. This states combination has a low scattering length, which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.

After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length 3322 hyperfine combination. To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $|F=3,m_F=3\rangle_{Cs}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer. This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.

@@

%% Transfer scheme
After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer. The pulse sequence for this step is shown in Fig.~\ref{f-raman}B. Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time (also minimize source of scattering). After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
%\todo{clarify coprop of Raman beam?}

@@

Next, we discuss the dependencies of the Raman Rabi frequency. The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}?). The atomic matrix element, $\Omega_a$, is proportional to the the short range atomic wavefunction amplitude, which scales as $ P^{0.375} $ for weakly interacting particles. However, due to the strong interaction between the two atoms, this approximation breaks down. Instead, theory calculation shows that the scaling is very well approximated by $ P^{0.29} $ within the range of confinement in our experiment. Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$, which agrees with our experimental result. Similar to the light shift, there is also a background component and a $v=0$ component in the Raman Rabi frequency. The $v=0$ component predicts a up leg Rabi frequency of $...$ which is consistent with theory. Unfortunately, the background Raman Rabi frequency cancels the Rabi frequency for red detuning Raman transition which is one of the factors that decreases our transfer efficiency. (need blue side?)
% I think we should include some takeaway from this paragraph as well, otherwise it may not be clear what the point is. Maybe something like, "Based on these analyses, the Rabi frequencies agree with theory. Thus, the high scattering rate to raman rabi frequency ratio is caused by larger than expected scattering, which we discuss next"
